Draft Exploration

### 2020-04-07 draft_exploration.Rmd
made function to graph distribution of debut age

top_20_hs %>%
  ggplot() +
  geom_col(aes(x = high_level, y = y, fill = signed), position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_light() +
  labs(
    x = "Peak Baseball Level Reached",
    y = "Percentage",
    signed = "Signed?",
    title = "Distribution of Peak Baseball Career Level of High School Picks",
    subtitle = "Grouped by whether or not the player signed out of high school"
  )

@@

peak_level(max_round = 20, startyear = 1990, endyear = 2011, min_round = 10)
```

>>>>

top_20_hs %>%
  ggplot() +
  geom_col(aes(x = high_level, y = y, fill = signed), position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_light() +
  labs(
    x = "Peak Baseball Level Reached",
    y = "Percentage",
    fill = "Signed?",
    title = "Distribution of Peak Baseball Career Level of High School Picks",
    subtitle = "Grouped by whether or not the player signed out of high school"
  )

@@

peak_level(max_round = 20, startyear = 1990, endyear = 2011, min_round = 1)
```

debut_age <- function(max_round, startyear, endyear, min_round = 1) {

debut <- master %>%
  filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
  filter(draft_round >= min_round & draft_round <= max_round & year >= startyear & year <= endyear) %>%
  group_by(signed, debut) %>%
  summarize(n = n()) %>%
  group_by(signed) %>%
  mutate(y = n/sum(n))

debut %>%
  ggplot(aes(x = debut, y = y, color = signed)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_x_continuous(breaks = c(18:30)) +
  theme_light() +
  labs(
    x = "Age During Debut Season",
    y = "Percentage",
    color = "Signed?",
    title = "Distribution of Debut Season Age of High School Picks",
    subtitle = "Grouped by whether or not the player signed out of high school"
  )

debut_age(max_round = 20, startyear = 1990, endyear = 2011, min_round = 1)
